Rotating Stars from \Kepler Observed with Gaia DR2

### 2018-05-21 paper/ms.tex
a couple words

indeed, 0.7solarmass star traced over its life in both panels doesnt quite make sense. 
inverting CMD into precise ages w/ Gaia beyond scope of this work, but this figure suggests the MS is too wide given a reasonable age range. consider: younger stars, presumably more metal rich, should be redder, moving in the wrong direction to the affect we see here. more colors and careful work needed... vertical action is OK for a star, but maybe some color impact we not considering.... hmm.

however, looking at 0.7M period vs lum evolution, we see that the period seems to also drop off too rapidly compared to a model. combining the MM09 spin-down formulae for a 0.7M star, with the MIST isochrone evolution, we see  the period range should go out to 60--80 days to get the right amplitude offset. That implies that at a given age (or vertical action), the stars are rotating {\it faster} than expected. this is similar to the broken spin-down model suggested by \citep{van-saders2016}, and is potentially the first confirmation of this observation.

>>>>

indeed, 0.7solarmass star traced over its life in both panels doesnt quite make sense. 
inverting CMD into precise ages w/ Gaia beyond scope of this work, but this figure suggests the MS is too wide given a reasonable age range. consider: younger stars, presumably more metal rich, should be redder, moving in the wrong direction to the affect we see here. more stellar masses and careful work needed... vertical spread in this parameter space is OK for a star, but maybe some color impact we not considering.... hmm.

however, looking at 0.7M period vs lum evolution, we see that the period seems to also drop off too rapidly compared to a model. combining the MM09 spin-down formulae for a 0.7M star, with the MIST isochrone evolution, we see  the period range should go out to 60--80 days to get the right amplitude offset. That implies that at a given age (or vertical offset), the stars are rotating {\it faster} than expected. this is similar to the broken spin-down model suggested by \citep{van-saders2016}, and is potentially the first confirmation of this observation.
